Misperceived Social Norms about Women Working Outside the Home and Its Effect on Women in Saudi Arabia

### 2024-02-14 outputs/paper/paper.qmd
modify footnote

---
title: "Misperceived Social Norms about Women Working Outside the Home and Its Effect on Women in Saudi Arabia"
author: 
  - Boxuan Yi
  - Ruoxian Wu
thanks: "Code and data are available at: https://github.com/ScarletWu/Misperceived-Social-Norms-Women-Working-Outside-the-Home-in-Saudi-Arabia. Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1557/"
date: "February 12, 2024"
date-format: long
abstract: "Husbands who hold guardianship and discourage their wives from working outside the home are often perceived as the main reason for the low female workforce participation in Saudi Arabia. We use data and surveys from the American Economic Association to analyze this perception, revealing that a majority of young husbands in Saudi Arabia privately support women working outside the home but underestimate the support of other men. This paper also discusses the positive effects brought about by correcting this misperception, strategies for reducing information intervention, and the unusual Saudi female employment rate during the pandemic."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Data
## Source
The paper used for replication is from American Economic Association, American Economic Review. The replication package is downloaded from Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia webpage, under Additional Materials. The original paper and its replicated package can be found here: https://www.aeaweb.org/articles?id=10.1257/aer.20180975

>>>>

---
title: "Misperceived Social Norms about Women Working Outside the Home and Its Effect on Women in Saudi Arabia"
author: 
  - Boxuan Yi
  - Ruoxian Wu
thanks: "Code and data are available at: https://github.com/ScarletWu/Misperceived-Social-Norms-Women-Working-Outside-the-Home-in-Saudi-Arabia. Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1557/. The original paper and its replicated package can be found here: https://www.aeaweb.org/articles?id=10.1257/aer.20180975."
date: "February 12, 2024"
date-format: long
abstract: "Husbands who hold guardianship and discourage their wives from working outside the home are often perceived as the main reason for the low female workforce participation in Saudi Arabia. We use data and surveys from the American Economic Association to analyze this perception, revealing that a majority of young husbands in Saudi Arabia privately support women working outside the home but underestimate the support of other men. This paper also discusses the positive effects brought about by correcting this misperception, strategies for reducing information intervention, and the unusual Saudi female employment rate during the pandemic."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Data
## Source
The paper used for replication is from American Economic Association, American Economic Review. The replication package is downloaded from Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia webpage, under Additional Materials.
